---
title: "p8015_hw6_tl2882"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(modelr)

set.seed(1)
```

# Problem 1

## Tidy data
```{r tiydata, message=FALSE}
data = 
  read_csv("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv") %>% 
  unite(city_state, city, state, sep = ", ") %>% 
  filter(!city_state %in% c("Dallas, TX", "Phoenix, AZ", "Kansas City, MO", "Tulsa, AL")) %>% 
  mutate(bi_disposition = as.numeric(disposition == "Closed by arrest")) %>% 
  mutate(victim_race = ifelse(victim_race == "White", "white", "non-white") ) %>% 
  mutate(victim_race = fct_relevel(victim_race, "white")) %>% 
  mutate(victim_age = as.numeric(victim_age))
```

## Model for Baltimore, MD

```{r Model_for_Baltimore}
model = glm(bi_disposition ~ victim_age + victim_sex + victim_race, 
            data = filter(data, city_state == "Baltimore, MD"), family = binomial(link = "logit"))
result = broom::tidy(model, conf.int = TRUE)

result %>% 
  filter(term == "victim_racenon-white") %>%
  mutate(odds_ratio = exp(estimate), 
         conf_low = exp(conf.low), conf_high = exp(conf.high)) %>% 
  select(odds_ratio, conf_low, conf_high) %>% 
  knitr::kable()
```

This is the estimate and confidence interval of the adjusted odds ratio for solving homicides comparing non-white victims to white victims keeping all other variables fixed.

## Model for each city

```{r fitmodel, warning=FALSE}
data_results = 
  data %>% 
  group_by(city_state) %>% 
  nest() %>% 
  mutate(models = map(data, ~glm(bi_disposition ~ victim_age + victim_sex + victim_race, 
                                data = .x, family = binomial(link = "logit")))) %>% 
  mutate(results = map(models, broom::tidy)) %>% 
  mutate(results_ci = map(models, broom::confint_tidy)) %>% 
  select(-data, -models) %>% 
  unnest() 
```

```{r Model_for_all}
results_ci = 
  data_results %>% 
  filter(term == "victim_racenon-white") %>% 
  mutate(odds_ratio = exp(estimate), 
         conf_low = exp(conf.low), conf_high = exp(conf.high)) %>% 
  select(city_state, odds_ratio, conf_low, conf_high)

results_ci
```

This is the estimate and confidence interval of the adjusted odds ratio for solving homicides comparing non-white victims to white victims keeping all other variables fixed.

### Plot

```{r}
results_ci %>% 
  mutate(city_state = fct_reorder(city_state, odds_ratio)) %>%
  ggplot(aes(x = city_state, weight = odds_ratio)) +
    geom_bar() + 
    geom_errorbar(aes(ymin = conf_low, ymax = conf_high), width = 0.5) +
    labs(title = "The estimates ORs and CIs for each city", y = "Proportion") +
    theme(axis.text.x = element_text(angle = -90))
```

This is the plot that shows the estimated ORs and CIs for each city

# Problem 2

## Tidy data
```{r tiydata2, message=FALSE}
data_baby = 
  read_csv("http://p8105.com/data/birthweight.csv") %>% 
  mutate(babysex = as.factor(recode(babysex, "1" = "male", "2" = "female"))) %>% 
  mutate(frace = as.factor(recode(frace, "1" = "White", "2" = "Black", "3" = "Asian", "4" = "Puerto Rican",
                                  "8" = "Other", "9" = "Unknown"))) %>% 
  mutate(mrace = as.factor(recode(mrace, "1" = "White", "2" = "Black", "3" = "Asian", "4" = "Puerto Rican",
                                  "8" = "Other"))) %>% 
  mutate(malform = as.factor(recode(malform, "0" = "absent", "1" = "present")))

sum(is.na(data_baby))
```

I converted numeric to factor where appropriate, and checked that there are no missing data.
