---
title: "p8015_hw6_tl2882"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(modelr)

set.seed(1)
```

# Problem 1

## Tidy data
```{r tiydata, message=FALSE}
data = 
  read_csv("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv") %>% 
  unite(city_state, city, state, sep = ", ") %>% 
  filter(!city_state %in% c("Dallas, TX", "Phoenix, AZ", "Kansas City, MO", "Tulsa, AL")) %>% 
  mutate(bi_disposition = as.numeric(disposition == "Closed by arrest")) %>% 
  mutate(victim_race = ifelse(victim_race == "White", "white", "non-white") ) %>% 
  mutate(victim_race = fct_relevel(victim_race, "white")) %>% 
  mutate(victim_age = as.numeric(victim_age))
```

## Model for Baltimore, MD

```{r Model_for_Baltimore}
model = glm(bi_disposition ~ victim_age + victim_sex + victim_race, 
            data = filter(data, city_state == "Baltimore, MD"), family = binomial(link = "logit"))
result = broom::tidy(model, conf.int = TRUE)

result %>% 
  filter(term == "victim_racenon-white") %>%
  mutate(odds_ratio = exp(estimate), 
         conf_low = exp(conf.low), conf_high = exp(conf.high)) %>% 
  select(odds_ratio, conf_low, conf_high) %>% 
  knitr::kable()
```

This is the estimate and confidence interval of the adjusted odds ratio for solving homicides comparing non-white victims to white victims keeping all other variables fixed.

## Model for each city

```{r fitmodel, warning=FALSE}
data_results = 
  data %>% 
  group_by(city_state) %>% 
  nest() %>% 
  mutate(models = map(data, ~glm(bi_disposition ~ victim_age + victim_sex + victim_race, 
                                data = .x, family = binomial(link = "logit")))) %>% 
  mutate(results = map(models, broom::tidy)) %>% 
  mutate(results_ci = map(models, broom::confint_tidy)) %>% 
  select(-data, -models) %>% 
  unnest() 
```

```{r Model_for_all}
results_ci = 
  data_results %>% 
  filter(term == "victim_racenon-white") %>% 
  mutate(odds_ratio = exp(estimate), 
         conf_low = exp(conf.low), conf_high = exp(conf.high)) %>% 
  select(city_state, odds_ratio, conf_low, conf_high)

results_ci
```

This is the estimate and confidence interval of the adjusted odds ratio for solving homicides comparing non-white victims to white victims keeping all other variables fixed.

### Plot

```{r}
results_ci %>% 
  mutate(city_state = fct_reorder(city_state, odds_ratio)) %>%
  ggplot(aes(x = city_state, weight = odds_ratio)) +
    geom_bar() + 
    geom_errorbar(aes(ymin = conf_low, ymax = conf_high), width = 0.5) +
    labs(title = "The estimates ORs and CIs for each city", y = "Proportion") +
    theme(axis.text.x = element_text(angle = -90))
```

This is the plot that shows the estimated ORs and CIs for each city

# Problem 2

## Tidy data
```{r tiydata2, message=FALSE}
data_baby = 
  read_csv("http://p8105.com/data/birthweight.csv") %>% 
  mutate(babysex = as.factor(recode(babysex, "1" = "male", "2" = "female"))) %>% 
  mutate(frace = as.factor(recode(frace, "1" = "White", "2" = "Black", "3" = "Asian", "4" = "Puerto Rican",
                                  "8" = "Other", "9" = "Unknown"))) %>% 
  mutate(mrace = as.factor(recode(mrace, "1" = "White", "2" = "Black", "3" = "Asian", "4" = "Puerto Rican",
                                  "8" = "Other"))) %>% 
  mutate(malform = as.factor(recode(malform, "0" = "absent", "1" = "present")))

sum(is.na(data_baby)) # 0 means no "TRUE"
```

I converted numeric to factor where appropriate, and checked that there are no missing data.

## Model Selection

I use stepwise regreession learned in "Biostatistical Methods" class.
"Step" function uses AIC criterion for covariates selection.
This methods develops a sequence of regression models, at each step adding or deleting a covariate.

```{r stepwise}
fit  = lm(bwt ~ ., data = data_baby)
step(fit, direction = 'backward')
```

So my model is:
```{r my_model}
model1 = lm(formula = bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + mheight + mrace + parity + ppwt + smoken, data = data_baby)
```

### Plot

```{r plot2}
data_baby %>% 
  add_predictions(model1) %>% 
  add_residuals(model1) %>% 
  ggplot(aes(x = pred, y = resid)) +
    geom_point(alpha = 0.1) +
    labs(title = "Residuals against Fitted values", x = "Fitted values", y = "Residuals")
```

The plot is used to detect unequal error variance (heteroscedasticity) and outliers.

Ideally, we would like to see that:

• Residual values bounce around 0

• Residuals form a horizontal ‘band’ around zero: above and below (indication of equal variance)

• No ‘unusual’ values stand out from the random pattern (indication of no potential outliers)

My model does't fit the ideal situation, which means my model is not very good.

## Compare models

```{r other_models}
model2 = lm(bwt ~ blength + gaweeks, data = data_baby)
# One using length at birth and gestational age as predictors (main effects only)

model3 = lm(bwt ~ bhead + blength + babysex + 
            bhead*blength + bhead*babysex + blength*babysex + bhead*blength*babysex, data = data_baby)
# One using head circumference, length, sex, and all interactions (including the three-way interaction) between these
```

### cross-validated prediction error

```{r cross-validated}
cv_df = 
  crossv_mc(data_baby, 100) %>% 
  mutate(model1 = map(train, ~lm(bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + mheight + 
                                   mrace + parity + ppwt + smoken, data = .x)),
         model2 = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
         model3 = map(train, ~lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + 
                                   blength*babysex + bhead*blength*babysex, data = data_baby), data = .x)) %>% 
  mutate(rmse1 = map2_dbl(model1, test, ~rmse(model = .x, data = .y)),
         rmse2 = map2_dbl(model2, test, ~rmse(model = .x, data = .y)),
         rmse3 = map2_dbl(model3, test, ~rmse(model = .x, data = .y)))

cv_df %>% 
  select(starts_with("rmse")) %>% 
  gather(key = model, value = rmse) %>% 
  mutate(model = str_replace(model, "rmse", "model"),
         model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```

In these three models, my model has lowest RMSE which means it is the best among three models. 
But actually, all three models have high RMSE. We should make futher improvements to get a better model. 